Out-of-Sample Comparisons of Overfit Models

### 2013-10-23 paper.tex
Fix scale factor in proof of convergence of centering terms
The exisitng proof of Lemma 1, convergence of the centering terms, has
an incorrect scale term P^{-1/2}; this commit removes it.

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.
  Moreover,
  \begin{align*}
    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
  \end{align*}
  for large enough $T$, where $S = R,T$, $i = 1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
  Additionally, the Euclidean norms of the pseudo-true coefficients,
  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
  $|\theta_2|_2 = O(1)$.
\end{asmp}

@@

We can see that these conditions are trivially satisfied when the
underlying series are i.i.d.\ Normal and the regression includes a
constant.
\begin{example}
  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
  uniformly positive definite, then
  \begin{equation*}
    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
  \end{equation*}
  and the regression constant is
  \begin{equation*}
    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
  \end{equation*}
  where both of these terms follow directly from the normality
  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
  N(0, v^2)$ (independent of $x_t$) with
  \begin{equation*}
    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
  \end{equation*}
  Then we have
  \begin{equation*}
    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
    = v^2 X_{T}'X_{T}
  \end{equation*}
  and
  \begin{equation*}
    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
    \,\Big|\, X_{R}'X_{R} \Big)\Big) = P v^2 \E x_t x_t'.
  \end{equation*}

  So the conditions amount to restrictions on the eigenvalues of
  $X_T'X_T$, which are familiar from general \ols.
\end{example}

@@

For~\eqref{eq:20}, observe that
\begin{align*}
  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
  &\quad+ \| x_i^{*\prime}
  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
  \eb_{iR} ] \|_2 \big).
\end{align*}
The first term in the upper bound satisfies
\begin{align*}
  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
  &= \E \tr\big( x_i^* x_i^{*\prime}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\
  &\leq \eigen_{K_i}(\E x_i x_i')
  \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
  X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
  & \quad \times \Big\|\sum_{j=1}^{K_i}
  \eigen_j^2((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \Big\|_{3/2}
\end{align*}

By Assumption~\ref{asmp-2},
\begin{equation*}
  \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
  X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(T).
\end{equation*}
Also, $(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $P$ and
its eigenvalues are bounded by those of $(X_{iR}'X_{iR})^{-1}$, which
are $O_{L_2}(1/R)$ by Assumption~\ref{asmp-2} as well, so
\begin{align*}
  \Big\|\sum_{j=1}^{K_i}
  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
  &= O(P/R^2)
\end{align*}
proving that
\begin{equation*}
  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
\end{equation*}

A similar argument proves that
\begin{equation*}
  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
\end{equation*}
completing the proof.
\qed

>>>>

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.  The
  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
  Moreover, there exists a finite $\Delta$ such that $\| x_{it}'x_{it}
  \|_3 \leq K_i \Delta$,
  \begin{align*}
    \lVert \eigen_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
    S_{T}\, \Delta, & \lVert
    \eigen_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
    \rVert_{3} &\leq S_{T}\, \Delta, \\
    \lVert \eigen_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
    \rVert_{3} &\leq \Delta/S_{T}, & \lVert
    \eigen_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
    &\leq \Delta/S_{T},
  \end{align*}
  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
  1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
  \text{and} \qquad
  \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
\end{asmp}

@@

@@

For~\eqref{eq:20}, observe that
\begin{align*}
  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
  &\quad+ \| x_i^{*\prime}
  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
  \eb_{iR} ] \|_2 \big).
\end{align*}
The first term in the upper bound satisfies
\begin{align*}
  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
  &= \E \tr\big( x_i^* x_i^{*\prime} X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2 \big) \\
  &\leq \eigen_{K_i}(\E x_i x_i') \E \Big|  \eigen_{K_i}(X_{iT}' \eb_{iT}
  \eb_{iT}' X_{iT}) \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
  (X_{iT}'X_{iT})^{-1}) \Big| \\
  &= O(T) \, \Big\| \sum_{j=1}^{t-R} \eigen_j^{-2}(X_{iR}'X_{iR}) \Big\|_{3/2} \\
  &= O(P^2/R)
\end{align*}
The second equality holds because $\eigen_{K_i}(X_{iT}' \eb_{iT}
\eb_{iT} X_{iT}) = O_{L_{3}}(T)$ by assumption and
$(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $t-R$ with
eigenvalues bounded by those of $(X_{iR}'X_{iR})^{-1}$.

A similar argument proves that
\begin{equation*}
  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
\end{equation*}
as well, completing the proof.
\qed
